Naming Anonymous JavaScript Functions

### 2011-04-06 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
first pass on sections 4.0, 4.1 and 4.2

\section{Introduction}
The unique and important role of JavaScript in web programming is undeniable. Along with the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site. This language is used by all of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}. It is very likely that JavaScript keeps this crucial role for the next few years or even the next decade. Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing. Morover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards}. There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.

To cope with these large and sophisticated systems, JavaScript developers turn to better development tools. These tools analyze then represent the program in ways that the developer might only be able to imagine through substaintial time-consuming reading of source code.  One prime example is a runtime debugger: the developer can halt a running program and examine the program state and execution call stack. All of these tools need to express program artifacts in a compact way the developer can understand.  For example, the debugger needs to present the execution call stack so the developer can understand which functions are currently active.  Obviously a particularly good compact representation would be a name given by the developer in the source code. However, the JavaScript language itself does not require names for many program artifacts and -- as we shall see -- nameless or anonymous artifacts are more common than named ones. Anonymous artifacts prevent tools from communcating effectively with developers.

Among program artifacts, functions are central to program comprehension in JavaScript. In addition to the their role in the execution stack, they are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a closure scope (module) or even  passed as an argument in a function call. However, functions can be defined and created without a name or identifier.

In this paper, we analyze function creation and consumption in ten large, well-known projects. We show that within these projects less than 7\% of the function objects are named. We propose an automated approach based on extracted data from the source code for naming JavaScript functions. The candidate function names can be used in debuggers for more descriptive object summaries and callstack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.

@@

If you are unfamilar with JavaScript or other functional programming languages, you might imagine that developers would naturally select the form with names, simply as an organizational tool. However this is not the case. Functions in JavaScript are first-class objects. They can be assigned to any variable or object property, or passed as an argument to a function. Consequently JavaScript programmers can use this constructs to organize their thinking about the program, without the use of function names.

So what do JavaScript developers do in practice?  To get empirical evidence we analyzed the source code of ten well-known JavaScript projects. For every project, the total number of functions and the number of functions with an identifier are collected (Table~\ref{js-functions}). The average ratio of named functions to all functions is less then 7 percent and excepting one project (Prototype), the ratio does not exceed 13 percent. )Our analysis does not include the functions defined by dynamically created evaluated scripts created by {\small\texttt{eval}} function). Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor. Therefore, we conclude that a large proportion of JavaScript functions are anonymous.

\begin{table}
\centering
\scalebox{0.9}{
  \begin{tabular}{ | l | l | l | l | l |}
  \hline
   Project & Description & Total & Named \\ 
  \hline 
   Closure & Google Web Library & 9195 & 208(2\%) \\ 
  \hline 
   DoJo & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
  \hline 
   ExtJS & JavaScript Framework & 37717 & 1184(3\%) \\ 
  \hline 
   Firebug & Web Development Tool & 3424 & 406(11\%) \\ 
  \hline 
   jQuery & JavaScript Library & 422 & 23(5\%) \\ 
  \hline 
   MochiKit &  JavaScript Library & 1866 & 37(1\%) \\ 
  \hline 
   MooTools & JavaScript Framework & 625 & 7(1\%) \\ 
  \hline 
   Prototype & JavaScript Framework & 645 & 203(31\%) \\ 
  \hline 
   Scriptaculous &  JavaScript Library & 1092 & 208(19\%) \\ 
  \hline 
   YUI &  Yahoo UI Library & 22346 & 922(4\%) \\ 
  \hline 
   All &  & 96008 & 6008(6.3\%) \\ 
  \hline 
  \end{tabular}
  }
\caption{The total number of functions and the number of named functions in ten famous JavaScript projects.}
\label{js-functions} 
\end{table}

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{pic/chrome-objects.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{pic/fbug-objects.jpg}}}
\caption{The screenshot of veriables view of Google Chrome and Firebug JavaScript debuggers displaying the same program state.}
\label{debuggers-objects}
\end{figure*}

% JJB TODO
% It is common that the same function is called by various names in different contexts. 
%Therefore, it is usually very difficult to recall the function operation from its local name. 
%Developers have usually the option to look at the function code, but it becomes tedious
% and time-consuming when developer has to do it over and over again.

%Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} 
%object is created. Notice that, depending on the times a function definition is evaluated, 
%zero to many {\small\texttt{Function}} objects can be created from the same definition. 
%To classify {\small\texttt{Function}} objects created by the same code, we call every 
%script defines a function as a \textit{function body}.

To understand the consequences of anonymous funcitons on development tools we will focus on one example, the impact on debuggers.
Two main issues apear in debuggers due to the lack of function name. First, object constructor name, which can faciliate understanding the object value, is not available in the object summary. Second, the callstack view is usually full of \textit{anonymous} functions and therefore much less informative. We disscuss these issues in the next two subsections.

Figure~\ref{js-code} demonstrates an excerpt of a JavaScript code. We set a breakpoint on line 13 and examin the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}. However, Google Chrome debugger shows the general class of {\small\texttt{Object}} as the summary for both objects. The developer has to expand the object nodes to recognize their similarities and differences. Firebug classify objects in the same general class, but includes some of the object properties in the summary. These additional properties may hint developer about the object structures. {\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain the debuggers' behaviour; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.

@@

\begin{lstlisting}[frame=single, language=myLang]
9  var main = function() {         // main<
10   return function() {           // main
11     var foo = new FOO("a");
12     var bar = new BAR("b");
13     var result = op(
14       function(value){          // main</result<
15         return value;
16        });
17   }
18 }();
19 var FOO = function(a) {         // FOO
20   this.a = a;
21 }
22 var BAR = function(b) {         // BAR
23   this.b = b;
24 }
25 var op = function() {           // op<
26   var local;
27   return function(callBack) {   // op
28     local++;
29     return callBack(local);
30   }
31 }();
\end{lstlisting}
%\end{verbatim}}
\caption{An excerpt of a JavaScript code.}
\label{js-code}
\end{figure}

\subsection{Anonymous Function Names in Callstack View}
To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debugger and Firebug. The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms. Google chrome shows \textit{anonymous} as the name of all functions excepting the first one. Firebug performs better by guessing three function names but it still fails in one case. In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.13\textheight]{pic/chrome-callstack.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.13\textheight]{pic/fbug-callstack.jpg}}}
\caption{The screenshot of callstack view of Google Chrome and Firebug JavaScript debuggers paused at the same breakpoint.}
\label{debuggers-callstack}
\end{figure*}

Two other pieces of information which are important at function calls are {\small\texttt{this}} and argument values. In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called. The {\small\texttt{this}} value is missed in both views. The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.

\section{Discussion}
The anonymous functions problem is discussed in several articles and forums on the web \cite{DisplayName, Zaytsev}. Different solutions have been proposed and discussed by practitioners. A basic solution is a mechanism for naming functions by developers without affecting the variables in scopes. For example, a new property (e.g., \textit{displayName}) in the function object can be used for storing the function name, or the function name can be defined by an annotation. Although these solutions may help, they cause developers extra work.

We instead propose an almost automated approach for naming all functions by anlyzing the source code. Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.

\subsection{What Makes a Good Function Name?}
A function name is basicly used to assist the developer to recall or understand the function behaviour. For a dveloper who is already familiar with the function, it works more like an identifier. However, this identifier should be easily recognized by the developer. For example, a naive proposal for the function name is a combination of the function file name and its first line number. Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.

 On the other hand, for a devloper who does not know the function, a function name should explains the function behaviour, or an abstraction of the function behaviour, or why/where the function is used/defined (e.g., to create the object \textit{foo}). A function name must not be too long that can not be displayed or read by the developer. For example, the function body explains the function behaviour well however it is not an appropriate function name.

\subsection{What Should be Named?} %// Function Object or Function Body}%What Should be Named?}
In JavaScript, functions can be accessed and changed like a regular object. Two function objects which are created from the same function body may have different properties. They also may have different enclosing scopes and therefore different behaviours. The question arises here is which one should be named, the function body or the function object? Although the actual enclosing scopes are not known until the function object creation, their structure can be almost known from the enclosing source code. Therfore the general function behaviour is mainly dependent to its function body and the enclosed function bodies.

\subsection{Context, Package and Function Names}
JavaScript does not support a standard packageing mechanism to be used for modular programming. Scripts are loaded from different files and executed within the same or different global objects. Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library. The same mechanism is reused for defining subpackages. As the project size and the number of functions increases, the short function name will not be enough for recognizing the function. The developer also wants the class or the module contains the function. In addition to the package name, knowning the context (the enclosing function body) that contains the function can help in better understanding the function behaviour.

@@

\section{Automated Funcation Naming}
%	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code. Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
  Developers usually understand and refer to function objects by aliases they use to access them. This fact particularly holds for permanent function objects such as classes and utility functions. However, functions with shorter lifetimes such as closures and callbacks are referred by their roles or purposes in the program. We employ these facts to construct an identifier for a function. We analyse the source code to locate alias(es) which the function object is assigned to. If the list of aliases is not empty we select the most appropriate one based on some ranking rules as the function name. Otherwise, we try to build a name based on the aliases that the function object somehow affect on their values. If there is no such alias then the function object is consumed as an argument in a chain of function calls that does not return any value or as a simple closure. In the case of function calls chain we use the most nested called function name for constructing the identifier. In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier. 
  Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects. These functions usually receive a string as the class name or function name. In our approach we need to get hint about these functions declarations. These hints can be usually described in simple regular expressions.

@@

\subsection{Examples}

   To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name. The first function in line 9 is called just after its creation and sets the {\small\texttt{main<}} value. We name this function {\small\texttt{main<}}. The symbol {\small\texttt{<}} shows that the function object contributes to the {\small\texttt{main}} value. To name the function object defined in line 10, we analyze the code to get the aliases used for the function object after its creation. Once the function object is created it is returned. As the enclosed function is just called after its creation we can continue our search for more aliases in the outer scope. The function object is assigned to {\small\texttt{main}}. Therfore we name it {\small\texttt{main}}.

   %For every function we first build a summary. The summary explains how the function object is used in relation to other identifiers. The first function defined in line 9 is called just after its creation and returns another function defined in line 10. The result is assigned to variable {\small\texttt{main}}. In this case the summary for the first function is {\small\texttt{main<}} as it produces the {\small\texttt{main}} object. The second function is directly assigned to {\small\texttt{main}} and thus its name will be {\small\texttt{main}}.
%    Therefore the internal function body is named {\small\texttt{main<}} as its corresponding function object is assinged to a variable with this name. What about the outer function itself? We name that {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.

The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}. This function contributes in producing the {\small\texttt{result}} value. Moreover, it is located inside another function which is named {\small\texttt{main<}}. Therefore, its full name will be {\small\texttt{main</result<}}. The symbol {\small\texttt{/}} is used to separate the context name from the function name. The functions defined in lines 19 and 22, are directly assigned to {\small\texttt{FOO}} and {\small\texttt{BAR}}. Therefore, the same names will be used for the functions. The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.

%Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
%We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}). A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}). However the latter requires knowning the function body of the called function which is not always possible.
%As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names. The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.

%Similar to the first two functions which are named {\small\texttt{mainClosure}} and {\small\texttt{main}},

@@

@@

\section{Conclusion}
We highlighted the problem of nameless functions in JavaScript. We studied 10 famous JavaScript projects source code. From
our study we suggested an automatic approach for naming nameless functions that can be used in debuggers for better representation of concrete
values and functions in callstack.

%\appendix
%\section{Appendix Title}

%This is the text of the appendix, if you need one.

>>>>

\section{Introduction}
The unique and important role of JavaScript in web programming is undeniable. Along with the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site. This language is used by all of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}. It is very likely that JavaScript keeps this crucial role for the next few years or even the next decade. Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing. Moreover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards}. There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.

To cope with these large and sophisticated systems, JavaScript developers turn to better development tools. These tools analyze then represent the program in ways that the developer might only be able to imagine through substantial time-consuming reading of source code.  One prime example is a runtime debugger: the developer can halt a running program and examine the program state and execution call stack. All of these tools need to express program artifacts in a compact way the developer can understand.  For example, the debugger needs to present the execution call stack so the developer can understand which functions are currently active.  Obviously a particularly good compact representation would be a name given by the developer in the source code. However, the JavaScript language itself does not require names for many program artifacts and -- as we shall see -- nameless or anonymous artifacts are more common than named ones. Anonymous artifacts prevent tools from communicating effectively with developers.

Among program artifacts, functions are central to program comprehension in JavaScript. In addition to their role in the execution stack, they are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a closure scope (module) or even  passed as an argument in a function call. However, functions can be defined and created without a name or identifier.

In this paper, we analyze function creation and consumption in ten large, well-known projects. We show that within these projects less than 7\% of the function objects are named. We propose an automated approach based on extracted data from the source code for naming JavaScript functions. The candidate function names can be used in debuggers for more descriptive object summaries and call-stack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.

%In this paper, we analyze function creation and consumption in ten famous project. We propose an automated approach based on extracted data from the source code for naming JavaScript functions. The candidate function names can be used in debuggers for more descriptive object summaries and callstack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.

%The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 7\%) of JavaScript functions are named.

@@

If you are unfamiliar with JavaScript or other functional programming languages, you might imagine that developers would naturally select the form with names, simply as an organizational tool. However this is not the case. Functions in JavaScript are first-class objects. They can be assigned to any variable or object property, or passed as an argument to a function. Consequently JavaScript programmers can use this constructs to organize their thinking about the program, without the use of function names.

So what do JavaScript developers do in practice?  To get empirical evidence we analyzed the source code of ten well-known JavaScript projects. For every project, the total number of functions and the number of functions with an identifier are collected (Table~\ref{js-functions}). The average ratio of named functions to all functions is less then 7 percent and excepting one project (Prototype), the ratio does not exceed 13 percent. Our analysis does not include the functions defined by dynamically created evaluated scripts created by {\small\texttt{eval}} function). Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor. Therefore, we conclude that a large proportion of JavaScript functions are anonymous.

\begin{table}
\centering
\scalebox{0.9}{
  \begin{tabular}{ | l | l | l | l | l |}
  \hline
   Project & Description & Total & Named \\ 
  \hline 
   Closure & Google Web Library & 9195 & 208(2\%) \\ 
  \hline 
   DoJo & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
  \hline 
   ExtJS & JavaScript Framework & 37717 & 1184(3\%) \\ 
  \hline 
   Firebug & Web Development Tool & 3424 & 406(11\%) \\ 
  \hline 
   jQuery & JavaScript Library & 422 & 23(5\%) \\ 
  \hline 
   MochiKit &  JavaScript Library & 1866 & 37(1\%) \\ 
  \hline 
   MooTools & JavaScript Framework & 625 & 7(1\%) \\ 
  \hline 
   Prototype & JavaScript Framework & 645 & 203(31\%) \\ 
  \hline 
   Scriptaculous &  JavaScript Library & 1092 & 208(19\%) \\ 
  \hline 
   YUI &  Yahoo UI Library & 22346 & 922(4\%) \\ 
  \hline 
   All &  & 96008 & 6008(6.3\%) \\ 
  \hline 
  \end{tabular}
  }
\caption{The total number of functions and the number of named functions (and percent named)  in ten large JavaScript projects. See appendix 1 for the project citations.}
\label{js-functions} 
\end{table}

@@

\begin{lstlisting}[frame=single, language=myLang]
9  var main = function() {         // main<
10   return function() {           // main
11     var foo = new FOO("a");
12     var bar = new BAR("b");
13     var result = op(
14       function(value){          // main/result<
15         return value;
16        });
17   }
18 }();
19 var FOO = function(a) {         // FOO
20   this.a = a;
21 }
22 var BAR = function(b) {         // BAR
23   this.b = b;
24 }
25 var op = function() {           // op<
26   var local;
27   return function(callBack) {   // op
28     local++;
29     return callBack(local);
30   }
31 }();
\end{lstlisting}
%\end{verbatim}}
\caption{An excerpt of a JavaScript code.}
\label{js-code}
\end{figure}

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{pic/chrome-objects.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{pic/fbug-objects.jpg}}}
\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-objects}
\end{figure*}

To understand the consequences of anonymous functions on development tools we will focus on one example, the impact on debuggers.
Two main issues appear in debuggers due to the lack of function name. First, object constructor name, which can facilitate understanding the object value, is not available in the object summary. Second, the call-stack view is usually full of \textit{anonymous} functions and therefore much less informative. We discuss these issues in the next two subsections.

Figure~\ref{js-code} demonstrates an excerpt of a JavaScript code. We set a breakpoint on line 13 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}. However, Google Chrome debugger shows the general class of {\small\texttt{Object}} as the summary for both objects. The developer has to expand the object nodes to recognize their similarities and differences. Firebug classify objects in the same general class, but includes some of the object properties in the summary. These additional properties may hint the developer about the object structures. {\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.

\subsection{Anonymous Function Names in Callstack View}
To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug. The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms. Google chrome shows \textit{anonymous} as the name of all functions excepting the first one. Firebug performs better by guessing three function names but it still fails in one case. In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.13\textheight]{pic/chrome-callstack.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.13\textheight]{pic/fbug-callstack.jpg}}}
\caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-callstack}
\end{figure*}

Two other pieces of information which are important at function calls are {\small\texttt{this}} and argument values. In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called. The {\small\texttt{this}} value is missed in both views. The {\small\texttt{arguments}} values is shown in Firebug, but it still suffers from the same issues as object summaries.

\section{Automated Function Naming}
The anonymous functions problem is discussed in several articles and forums on the web \cite{DisplayName, Zaytsev}. Different solutions have been proposed and discussed by practitioners. A basic solution is a mechanism for naming functions by developers without affecting the variables in scopes. For example, a new property (e.g., \textit{displayName}) in the function object can be used for storing the function name, or the function name can be defined by an annotation. Although these solutions may help, they cause developers extra work, the annotation may be incorrectly recognized in programs that use the same property name for another purpose, and maintenance of the debugger becomes more difficult once the call-stack names can be overridden by user code.

We instead propose an almost automated approach for naming all functions by analyzing the source code. Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.

\subsection{What Should Be Named?}

Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} 
object is created.  The definition may be evaluated multiple times, and depending on the times a function definition is evaluated, 
zero to many {\small\texttt{Function}} objects can be created from the same definition. 
Two function objects which are created from the same function body may have different object properties added at runtime. They also may have different enclosing scopes and therefore different behaviors.  Thus our first 
decision: do we try to name the {\small\texttt{Function}} objects or the source that defines them?

For the common use cases, the different {\small\texttt{Function}} objects are bound to one or more properties of objects. The  names of these properties inform the developer about the role of the function in the actions of the object.  To determine the actions of the functions in turn, the developer must read the function source (or perhaps its documentation). Our function names serve to recall or summarize that source or documentation for the developer. Therefore we seek to name the source, the content between the curly braces known as the \textit{FunctionBody} in the standard\cite{ECMA}.

After reflection the reader may be puzzled by the preceding claim. On the one hand we claim that the function object instance may be bound to properties in multiple objects and those property names are not helpful for naming. On the other hand we will shortly introduce an algorithm that uses a property name (in part) to name a \textit{FunctionBody}. Ultimately we are relying on a subtle characteristic of JavaScript programming: the first binding of a {\small\textit{Function}}  to an object property differs from all other bindings because it is located in text near the \textit{FunctionBody} and thus developers associate this first binding with the meaning of the {\small\textit{FunctionBody}}.

\subsection{What Makes a Good Function Name?}
A function name is basically used to assist the developer to recall or understand the function behavior. For a developer who is already familiar with the function, it works more like an identifier. However, this identifier should be easily recognized by the developer. For example, a naive proposal for the function name is a combination of the function file name and its first line number. Although it may work as an identifier, but it does not assist the developer to recall or understand the function behavior.

 On the other hand, for a developer who does not know the function, a function name should explains the function behavior, or an abstraction of the function behavior, or why/where the function is used/defined (e.g., to create the object \textit{foo}). A function name must not be too long that can not be displayed or read by the developer. For example, the function body explains the function behavior well however it is not an appropriate function name.

\subsection{Context, Package and Function Names}
JavaScript does not support a standard packaging mechanism to be used for modular programming. Scripts are loaded from different files and executed within the same or different global objects. Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library. The same mechanism is reused for defining subpackages. As the project size and the number of functions increases, the short function name will not be enough for recognizing the function. The developer also wants the class or the module contains the function. In addition to the package name, knowing the context (the enclosing function body) that contains the function can help in better understanding the function behavior.

@@

\section{Static  Function Object Consumption}

We call our automated naming solution "Static Function Object Consumption", since it relies only a parser (static) and it attempts to name function bodies by tracking the function object created from the body to where the object is 'consumed', for example by binding to an object property, variable reference, or function argument.
Static Function Object Consumption generalizes the built-in JavaScript naming and common, simple coding patterns like object property initializers and variable assignments typically recognized by developers as naming functions.
The built-in naming, a function declaration, binds a name in a scope to a function object created from the adjacent function body. For example, in  {\small\texttt{function foo() \{return 1;\}}}, the name  {\small\texttt{foo}} is bound the the function body in curly braces.
Object property initializers bind a object property name to a function created from an adjacent function body. For example,  {\small\texttt{var bar = \{foo: function()\{return 2; \}\}}}, sets {\small\texttt{bar.foo}} to a function object created from the body {\small\texttt{\{return 2;\}}}. While the language does not associate the function body with the property  {\small\texttt{bar.foo}}, a JavaScript developer would because the created function body initializes the property. Similarly, a varible name bound to a function object, such as {\small\texttt{var baz = function()\{return 3; \}}}, is naturally associated with the function body. All three of these simple cases share the character that a function body creates a function object which is then bound to an identifier.

Our algorithm applies the same logic: we follow the function object backwards through the code to create a name in cases where an identifier is not directly given in the code.
By 'backwards through the code' we mean that we parse the JavaScript and analyze the resulting syntax tree. For each function body, we walk up the tree looking for the constructs in table 2. As we describe in section XX, for every matching construct we record identifiers or expressions to use in constructing a name. 
Then we assemble a name using the expression-reduction rules outlined in section YY and the context naming rules in section ZZ. The result is a summary that contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanitory tokens. It compactly explains the function object creation, consumption and assignment. For the simple cases of function declaration, object property initialization, and variable initialization the algorithm gives the same results we described above.

%	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code. Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
%  Developers usually understand and refer to function objects by aliases they use to access them. This fact particularly holds for permanent function objects such as classes and utility functions. However, functions with shorter lifetimes such as closures and callbacks are referred by their roles or purposes in the program. We employ these facts to construct an identifier for a function. We analyze the source code and build a summary that explains the function object creation, consumption and assignment.
This summary which only contains identifiers (i.e., variable and property names) and strings available in the source code gives us the ingeredients for function identifier construction.

  %We analyse the source code to obtain the alias(es) that used for the function object or  is assigned to. If the list of aliases is not empty we select the most appropriate one based on some ranking rules as the function name. Otherwise, we try to build a name based on the aliases that the function object somehow affect on their values. If there is no such alias then the function object is consumed as an argument in a chain of function calls that does not return any value or as a simple closure. In the case of function calls chain we use the most nested called function name for constructing the identifier. In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier.

@@

\subsection{Example}

To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name.

The first function on line 9 is called just after its creation (see line 18) and the return sets the {\small\texttt{main}} value. We can explain the function object consumption after its creation in two steps: 1) the function object is called (case 9 in table 2). 2) the result is assigned to {\small\texttt{main}} (case 6 in table 2). This differs from the simple variable assignment case: the value of {\small\texttt{main}} is not a function object but rather the return value of a function object.   We summarize this by saying that the result object is produced by the function object or the function object contributed to the {\small\texttt{main}} value and we write it {\small\texttt{main<}}, where the symbol {\small\texttt{<}} indicates "contributes to".

The function in line 10 is returned just after its creation. However, as the enclosing function is just called after its creation we can follow the function object flow in the enclosing scope and see that the function object is assigned to {\small\texttt{main}}. The summary of the function object consumption will be: 1) the function object is returned (case 10, table 2), 2) the function object is assigned to {\small\texttt{main}} (case 6 table 2). As the function object is directly assigned to this variable we name the function {\small\texttt{main}}. BUT I DON"T GET IT.

The third function, line 14, is passed to a function {\small\texttt{op}} on line 13, within the body of the function we named {\small\texttt{main}} . Here 1) the function object is passed as an argument to function {\small\texttt{op}} (case 11), 2) The call result is assigned to {\small\texttt{result}} (case 6). If we simply put of identifiers in this summary together we get {\small\texttt{main/result<op()}}. The first part before slash  shows the context name (the enclosing function name) for this function.  However, the function names (here {\small\texttt{op()}}) usually give an indirect information (e.g., role) about the function object. Therefore, as we explain in the next subsection, we ignore them if other kind of identifiers (e.g., variable and property name) are available in the summary. After dropping {\small\texttt{op}}, we will have {\small\texttt{main/result<}}. Eliding identifiers is important to avoid creating long, unweildy names.

The next two functions, {\small\texttt{FOO}} on line 19 and {\small\texttt{BAR}} on line 22 are simple examples of case 6.  The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.

@@

\subsection{Overview of the Function Object Consumption Algorithm}
The algorithm starts by parsing the JavaScript code in to a syntax tree\cite{XX}, then iterating over each function body in the tree. For each function body look for the path of the function object from creation to consumption. We process the abstract syntax tree from the function definition node recursively back to the root node in the enclosed function. On each step we determine if the next node represents one of the cases presented in Table~\ref{table:function-types}. As we go upward in the tree, we keep identifiers and whether the object consumed is the same, part of, or contributed to the result object. Once the summary is ready we construct the identifier. The identifiers come from function calls (case 11) are ignored if there is any other type of identifier. Otherwise, only the closest function call identifier will be used. Nodes which are not one of the type specfied in Table~\ref{table:function-types} are ignored.

Note that two cases, one where the function is a top script element and the second where function is created by {\small\texttt{Function}} constructor do not appear in the table. The top script functions can not be anonymous and the functions defined by the constructor can be considered as a regular function body. Names which are specified with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifer in ~\ref{sec:general-element-naming}.

\subsection{Building a String from Arguments}

\subsection{Building a String from An Expression}

\subsection{Namer Functions}
Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects. These functions usually receive a string as the class name or function name. The number of namer functions is usually very limited for a specific project and can be provided to debugger by the developer. A namer function works like an assignment in the summary.

\subsection{Temporary Variables} %aliases for the same object

\subsection{Context Name}

\subsection{Functions created by {\large \texttt{eval()}}}
The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is avaialble. However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.

%\section{Improved by Runtime Data}
%\subsection{Naming Functions in Call Stack}

\subsection{Object Creation}

@@

%JavaScript, unlike many traditional object oriented languages such as Java and C\#, does not have classes, and does not encourage encapsulation or even structured programming. JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}. As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations. For example, the value of a variable can be a primitive value, an object with any structure or even a function. One callsite may invoke different function bodies with various number of arities that none of them can be understood from the code. Therefore, the lack of descriptive data in JavaScript code is the most fundumental issue in enhancing JavaScript tool support.

Catching errors early (i.e., before or at the compilation time) is an important feature for development environments. It can save developers' time, prevent bugs and improve the program quality. However, many errors can not be recognized without a strong typing stystem. To attack this issue a few static typing systems have been proposed for JavaScript \cite{Anderson, Anderson2, Heidegger, Thiemann}. These approaches discover the type of values and object structures for a variable by statically analyzing the source code and possible program control flows lead to the variable assignment. The discovered facts about variable types are not only useful for catching errors but to provide modern editing features such as auto-complete and refactoring in development environments. Moreover, the infered data can help in code comprehension if they are properly presented. Nevertheless, none of the mentioned approaches provided effective means for sharing this information with the developer. This leads us to another hidden issue for improving JavaScript development tools; Due to highly dynamism in JavaScript many elements are remained nameless. Therefore there is no common language between the tool and developer for referring to elements.
